``How Prolific Are You?": A Scientometric Analysis of Researchers

### 2018-12-09 paper/paper.tex
Updated paper with conclusion

@@

	Because DBSCAN requires an \textit{eps} parameter, we chose to find a reasonable guess. We did this by setting a threshold that no more than roughly 10\% of the points (we chose 60 points) should be in individual custers. We started with an initial \textit{eps} guess of 0.5 and made increments of 0.1 till this condition was satisfied.

@@

	\begin{tabular}{|c|c|c|c|}
		\hline 
		$C_1$ & $C_2$ & \textbf{95\% significant} & \textbf{90\% significant} \\ 
		\hline 
		-1 & 0 & 1.0 & 1.0 \\ 
		\hline 
		-1 & 1 & 0.857 & 0.857 \\ 
		\hline 
		-1 & 2 & 0.928 & 1.0 \\ 
		\hline 
		0 & 1 & 0.786 & 0.857 \\ 
		\hline 
		0 & 2 & 1.0 & 1.0 \\ 
		\hline 
		1 & 2 & 0.643 & 0.786 \\ 
		\hline 
	\end{tabular} 
	\begingroup
	\captionof{table}{Percentage of significant Welch's test p-values at 95\% and 90\% confidence levels}
	\endgroup
	\hfill\break

>>>>

	Our contributions are two-fold. First, we outline a systematic method to identify prolific authors based solely on data using two algorithms, and compare their results. Second, we illustrate an approach to choose an appropriate value of eps in DBSCAN by setting a threshold on the number of individual clusters formed.

@@

	Because DBSCAN requires an \textit{eps} parameter, we chose to find a reasonable guess. We did this by setting a threshold that no more than roughly 10\% of the points (we chose 60 points) should be in individual custers. We started with an initial \textit{eps} guess of 0.5 and made increments of 0.1 till this condition was satisfied. For all experiments, the minimum samples parameter was set to 5.

@@

	\begin{tabular}{|c|c|c|c|}
		\hline 
		$C_1$ & $C_2$ & \textbf{95\%} & \textbf{90\%} \\ 
		\hline 
		-1 & 0 & 1.0 & 1.0 \\ 
		\hline 
		-1 & 1 & 0.857 & 0.857 \\ 
		\hline 
		-1 & 2 & 0.928 & 1.0 \\ 
		\hline 
		0 & 1 & 0.786 & 0.857 \\ 
		\hline 
		0 & 2 & 1.0 & 1.0 \\ 
		\hline 
		1 & 2 & 0.643 & 0.786 \\ 
		\hline 
	\end{tabular} 
	\begingroup
	\captionof{table}{Fraction of significant Welch's test p-values at 95\% and 90\% confidence levels}
	\endgroup
	\hfill\break

	\section{Conclusion}
	We investigated the use of DBSCAN to identify prolific authors in the context of a scientometric dataset.

	Our experiments demonstrate the capability of our methods.  For the task of identifying prolific authors, both clustering algorithms produced similar results. For finding a suitable value of eps, to the best of our knowledge, we are the first to attempt to automate the process of searching by setting a threshold on the number of individual clusters. Our method of choosing eps produced clusters similar to those produced autonomously by Mean-Shift clustering, which lends credence to the efficacy of our approach.
